Deep Gaussian Processes and Hierarchical Modeling with Functional Data: A Case Study in Cosmological Power Spectra

### 2024-08-28 paper/main.tex
one typo, comment out missing figure

We compare our DGP.HM model to competing models with a simulation study, in which case the true curve is known. Following \cite{moran2024dpc}, we consider two functions (1 and 2) each with two variance specifications (settings ``A", ``B", \textcolor{blue}{, we can consider additional homoskedastic cases in the appendix if necessary}). \textcolor{blue}{Put in the details of the two functions, and the two variance specs.} The competing methods we consider are an out-of-the-box DGP fit using the \texttt{deepgp} package \citep{sauer2023active}, a heteroskedastic GP fit using the \textt{hetGP} package \citep{binois2018practical, binois2021hetgp}, as well as a deep process convolution (DPC) approach, which is utilized within Cosmic Emu \citep{moran2023mira}.

@@

\begin{figure}[ht]
    \centering
    \includegraphics[width=6in]{plot_warp_M001.png}
    \caption{Left: MCMC samples of $W$ for model M001 after burnin and thinning. Right: Corresponding 95\% credible intervals for $W$.}
    \label{fig:plot_warp}
\end{figure}

>>>>

We compare our DGP.HM model to competing models with a simulation study, in which case the true curve is known. Following \cite{moran2024dpc}, we consider two functions (1 and 2) each with two variance specifications (settings ``A", ``B", \textcolor{blue}{, we can consider additional homoskedastic cases in the appendix if necessary}). \textcolor{blue}{Put in the details of the two functions, and the two variance specs.} The competing methods we consider are an out-of-the-box DGP fit using the \texttt{deepgp} package \citep{sauer2023active}, a heteroskedastic GP fit using the \texttt{hetGP} package \citep{binois2018practical, binois2021hetgp}, as well as a deep process convolution (DPC) approach, which is utilized within Cosmic Emu \citep{moran2023mira}.

@@

%\begin{figure}[ht]
%    \centering
%    \includegraphics[width=6in]{plot_warp_M001.png}
%    \caption{Left: MCMC samples of $W$ for model M001 after burnin and thinning. Right: Corresponding 95\% credible intervals for $W$.}
%    \label{fig:plot_warp}
%\end{figure}
